Random Matrix Theory Tools for the Predictive Analysis of Functional Magnetic Resonance Imaging Examinations - Supplementary Material

### 2022-11-15 paper/paper/SPIE/supplementary.tex
[WIP]
finalize
tidy up and make corrections to paper

\documentclass{article}  % use this instead for A4 paper
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{authblk}
\usepackage{times}
\usepackage{float}
\restylefloat{table}  % https://stackoverflow.com/questions/1673942/latex-table-positioning
\usepackage{ifthen}
\usepackage{setspace}
\usepackage[super]{cite}[2003/11/04] % need vers. > 4.01
\usepackage{color}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{graphicx}
\graphicspath{ {./figures/} }
\usepackage{setspace}
\usepackage{tocloft}
\usepackage{doi}
\usepackage{csquotes}
\MakeOuterQuote{"}
\usepackage{pdflscape}
\usepackage{geometry}
\geometry{
  textwidth=11in,
  textheight=8.5in,
  headheight=0in,
  headsep=0in,
  marginparwidth=0in,
  papersize={11in,8.5in},
  left=0in,
  lmargin=0in,
  inner=0in,
  right=0in,
  rmargin=0in,
  outer=0in,
  top=0in,
  tmargin=0in,
  bottom=0in,
  bmargin=0in,
}

@@

\title{Supplementary Material}

\author[a]{Derek Berger}
\author[a,*]{Jacob Levman}
\author[b]{Gurpreet M. Matharoo}
\affil[a]{St. Francis Xavier University, Department of Computer Science, 4130 University Avenue, Antigonish, Canada, B2G 2W5}
\affil[b]{St. Francis Xavier University, ACENET, 4130 University Avenue, Antigonish, Canada, B2G 2W5}

>>>>

\documentclass{article}  % use this instead for A4 paper
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{authblk}
\usepackage{times}
\usepackage{float}
\restylefloat{table}  % https://stackoverflow.com/questions/1673942/latex-table-positioning
\usepackage{ifthen}
\usepackage{setspace}
\usepackage[super]{cite}[2003/11/04] % need vers. > 4.01
\usepackage{color}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{graphicx}
\graphicspath{ {./figures/} }
\usepackage{setspace}
\usepackage{tocloft}
\usepackage{doi}
\usepackage{csquotes}
\MakeOuterQuote{"}
\usepackage{pdflscape}
\usepackage{geometry}
\geometry{
  textwidth=11in,
  textheight=8.5in,
  headheight=0in,
  headsep=0in,
  marginparwidth=0in,
  papersize={11in,8.5in},
  left=0in,
  lmargin=0in,
  inner=0in,
  right=0in,
  rmargin=0in,
  outer=0in,
  top=0in,
  tmargin=0in,
  bottom=0in,
  bmargin=0in,
}
\usepackage[margin=1in]{caption}

@@

\title{Random Matrix Theory Tools for the Predictive Analysis of Functional Magnetic Resonance Imaging Examinations - Supplementary Material}

\author[a]{Derek Berger}
\author[b,c]{Gurpreet S. Matharoo}
\author[a*,d,e,f]{Jacob Levman}

\affil[a]{St. Francis Xavier University, Department of Computer Science, 4130 University Avenue, Antigonish, Nova Scotia, Canada, B2G 2W5}
\affil[b]{St. Francis Xavier University, ACENET, 4130 University Avenue, Antigonish, Nova Scotia, Canada, B2G 2W5}

\affil[c]{St. Francis Xavier University, Department of Physics, 4130 University Avenue, Antigonish, Nova Scotia, Canada, B2G 2W5}

\affil[d]{Martinos Center for Biomedical Imaging, 149 Thirteenth Street, Suite 2301, Charlestown, Massachusetts, United States, 02129}
\affil[e]{Harvard Medical School, Department of Radiology, 25 Shattuck Street Boston, Massachusetts 02115, United States, 02129}
\affil[f]{Nova Scotia Health Authority, Research Affiliate, Nova Scotia, Canada}
